DOpElib - Deal Optimization Environment

### 2012-07-11 Examples/Documentation/introduction.tex
Removed Makefile.dep from svn

>>>>

\section{FAQs}
\paragraph{1.) When building the library I get an error message:}
\begin{itemize}
\item {\bf unrecognized command line option "-std=gnu++0x"}\\
  This means that your compiler is too old. You can check the 
  version of your compiler using \texttt{g++ -v}. If the version is lower than
  \texttt{4.5} you need to get a newer compiler version.
\end{itemize}

\paragraph{2.) I have installed a new g++ compiler but g++ -v still finds the old one :}
\ \\
  This means that your computer does not find the new compiler. Try
  \texttt{which g++} to see whether it appears in the list of availiable 
  compilers (but is maybe too far in the back of the list.) Then you should 
  modify your \texttt{\$PATH} environment variable so that the new g++ compiler
  appears.

  If \texttt{which g++} only returns one g++ compiler, then probably you need to
  set an appropriate symlink.

  For example on Mac OSX you will find only one g++ compiler \texttt{/usr/bin/g++}
  which is in fact a symlink to \texttt{/usr/bin/g++-4.2}. Thus to change, the 
  desired behavior you should add a new link named \texttt{g++} in a directory 
  in front of \texttt{/usr/bin} or replace the symlink in \texttt{/usr/bin}
  with a link to the newer compiler which may be for instance located (macports 
  g++ 4.5 on OSX Lion) in \texttt{/opt/local/bin/g++-mp-4.5}. Make shure that 
  you add additional appropriate links to \texttt{gcc, cc, }and \texttt{c++}.
